A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-10 doc/draft-01-stokes/04numerical.tex
add figures
minor updates
update figure

We can obtain an a posteriori estimate of the
error in a computed root as follows.
%
Let $f$ denote an analytic function,
$P$ be the polynomial interpolant
of that function over some interval,
$\delta f = f-P$ be the difference,
and $k_\cheb$ denote a computed root
of $P$.
%
The algorithm used by \texttt{chebfun}
to approximate the roots of $P$ is
backward stable~\cite{noferini2017chebyshev}.
Therefore the error in the roots will be
small relative to the error of the fit and
we set $P(k_\cheb) = 0$ below.
%
Suppose that
$f(k_\cheb + \delta k) = 0$ for some
small $\delta k$. Then

@@

@@

We consider the barbell-shaped domain in \cref{fig:barbell}.
This domain is the union of a square of side-length 6,
a square of side-length 3, and a ``bridge'' connecting
them of height 1 and width 5/2.
%
For the sake of simplicity, we round the corners of the domain
to obtain a smooth object.
%
Applying the approach described in~\cite{epstein2016smoothed},
the corners of the domain are rounded by convolving with
the Gaussian kernel
\begin{equation}
  \nonumber
\phi(x) = \frac{1}{\sqrt{2\pi h}} e^{-x^2/(2 h^2)} \, ,
\end{equation}
with $h\approx 0.06$. This leaves the domain unperturbed
to high precision outside of a radius of $0.1$ around
each corner.
%
The eigenfunctions of such a domain display the well-known
localization property~\cite{trefethen2006computed}:
many of the eigenfunctions are approximately supported
within one of the squares.
%
We compute these eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$0.5 \leq k \leq 6.5$.

@@

We now consider the multiply-connected domain in
\cref{fig:many_holes}.
% 
The domain is defined by a smooth rectangular region
of width 3 and height 2,
with an array of randomly rotated ``starfish'' shapes
removed. 
%
Such shapes are of interest in
materials design and micro-fluidics \note{cite}.
%
We compute the eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$3 \leq k \leq 9$ (this range includes the smallest
eigenvalue).

>>>>

We can obtain an a posteriori estimate of the
error in a computed root as follows.
%
Let $f$ denote an analytic function,
$P$ be the polynomial interpolant
of that function over some interval,
$\delta f = f-P$ be the difference,
and $k_\cheb$ denote a computed root
of $P$ which is simple (i.e. assume
that $P'(k_\cheb) \ne 0$).
%
The algorithm used by \texttt{chebfun}
to approximate the roots of $P$ is
backward stable~\cite{noferini2017chebyshev}.
Therefore the error in the roots will be
small relative to the error of the fit and
we set $P(k_\cheb) = 0$ below.
%
Suppose that
$f(k_\cheb + \delta k) = 0$ for some
small $\delta k$. Then

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_barbell_001_bdry}
    \caption{A barbell-shaped domain.}
    \label{subfig:barbell_bdry}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_bdry}
    \caption{A domain with several inclusions.}
    \label{subfig:many_inclusions_bdry}
  \end{subfigure}
\end{figure}

@@

We consider the barbell-shaped domain in \cref{subfig:barbell_bdry}.
This domain is the union of a square of side-length 6,
a square of side-length 3, and a ``bridge'' connecting
them of height 1 and width 5/2.
%
For the sake of simplicity, we round the corners of the domain
to obtain a smooth object.
%
Applying the approach described in~\cite{epstein2016smoothed},
the corners of the domain are rounded by convolving with
the Gaussian kernel
\begin{equation}
  \nonumber
\phi(x) = \frac{1}{\sqrt{2\pi h}} e^{-x^2/(2 h^2)} \, ,
\end{equation}
with $h\approx 0.06$. This leaves the domain unperturbed
to high precision outside of a radius of $0.1$ around
each corner.
%
The eigenfunctions of such a domain display the well-known
localization property~\cite{trefethen2006computed}:
many of the eigenfunctions are approximately supported
within one of the squares.
%
We compute these eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$0.5 \leq k \leq 6.5$.

@@

We now consider the multiply-connected domain in
\cref{subfig:many_inclusions_bdry}.
% 
The domain is defined by a smooth rectangular region
of width 3 and height 2,
with an array of randomly rotated ``starfish'' shapes
removed. 
%
Such shapes are of interest in
materials design and micro-fluidics \note{cite}.
%
We compute the eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$3 \leq k \leq 9$ (this range includes the smallest
eigenvalue).
